### 2019-07-18 initial/notes.tex
toy problem 3 seems to have plausible agreement

We can add a tidal dissipation term; we write it in form
$\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
\hat{s}} = \epsilon\p*{\vec{l} - \p*{\vec{s} \cdot \vec{l}}\vec{s}}$. Expanding,
\begin{align}
    \p*{\rd{\hat{s}}{t}}_{tide} &= \epsilon \p*{\hat{z} - s_z\hat{s}}
        ,\nonumber\\
        &= \epsilon \p*{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p*{1 - s_z^2}
            \hat{z}}.
\end{align}
We run numerical simulations for weaker $\epsilon \ll \eta \ll 1$ and stronger
$\epsilon \lesssim \eta \ll 1$.

@@

Though this section is located before the weak tidal friction section, we
actually return to this second toy problem to get some practice on the Henrard
paper, to confirm the accuracy of our simulations compared to analytical
predictions, and to get some practice doing these new integrals. Consider the
dissipation-free Cassini state system with a small but constant $\pd{\eta}{t} =
\epsilon$. For clarity, the Hamiltonian is
\begin{equation}
    H = -\alpha\frac{\mu^2}{2} +
        \mu \cos I - \sin I \sqrt{1 - \mu^2} \cos \phi.
\end{equation}
This proves to be the algebraically easiest formulation, instead of using
$\eta$.

@@

>>>>

We can add a tidal dissipation term; we write it in form
$\p*{\rd{\hat{s}}{t}}_{tide} = \epsilon \hat{s} \times \p*{\hat{l} \times
\hat{s}} = \epsilon\p*{\vec{l} - \p*{\vec{s} \cdot \vec{l}}\vec{s}}$. Expanding,
\begin{align}
    \p*{\rd{\hat{s}}{t}}_{tide} &= \epsilon \p*{\hat{z} - s_z\hat{s}}
        ,\nonumber\\
        &= \epsilon \p*{-s_z s_x\hat{x} - s_zs_y\hat{y} + \p*{1 - s_z^2}
            \hat{z}}.\label{eq:p1_eom}
\end{align}
We run numerical simulations for weaker $\epsilon \ll \eta \ll 1$ and stronger
$\epsilon \lesssim \eta \ll 1$.

@@

\subsection{Using $\alpha = 1/\eta$}

Though this section is located before the weak tidal friction section, we
actually return to this second toy problem to get some practice on the Henrard
paper, to confirm the accuracy of our simulations compared to analytical
predictions, and to get some practice doing these new integrals. Consider the
dissipation-free Cassini state system with a small but constant
\begin{equation}
    \pd{\eta}{t} = \epsilon.\label{eq:p2_eom}
\end{equation}
For clarity, the Hamiltonian is
\begin{equation}
    H = -\alpha\frac{\mu^2}{2} +
        \mu \cos I - \sin I \sqrt{1 - \mu^2} \cos \phi.
\end{equation}
This proves to be the algebraically easiest formulation, instead of using
$\eta$.

@@

For reference, let's also write down the $B_i$ in the $\dot{\eta} = \epsilon
\eta$ case. First, $B_{+}$:
\begin{align*}
    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \eta \cos I\;\mathrm{d}\phi
            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
        &= 2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{align*}
Along the bottom leg, the first term changes signs (both integrals have their
paths flipped, but the sign of the second integral also changes), and so
\begin{equation}
    B_{\pm} = \pm 2\pi \epsilon \eta \cos I
        - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{equation}
Generally, since $\eta$ is small, $B_{+} + B_- < -\abs*{B_+}, -\abs*{B_-}$ which
implies guaranteed capture from both sides, as expected (note that in our actual
paper, we compute changes for $h \equiv H^{(0)} - H_4$, while here we compute
changes in $H_4 - H^{(0)}$, accounting for the change in sign).

\subsection{Toy Problem 3: Including Toy Tides}

Consider now the extended toy problem where we both include the tidal term
\autoref{eq:p1_eom} and adiabatic parameter variation \autoref{eq:p2_eom}. In
the interest of generality, we replace
\begin{equation}
    \rd{\eta}{\tau} = f \epsilon \eta,
\end{equation}
such that the two $\epsilon$-fast terms have a tunable relative strength
$f \sim 1$.

We can now compute the $\Delta_{\pm}$ changes in $h \equiv H^{(0)} - H_4$
(following my paper's convention, rather than those earlier in these notes),
which are:
\begin{equation}
    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
        16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
            \s*{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
\end{equation}
The two contributions are bracketed.
